---
title: "The R Package S3PL: A Tutorial"
output: 
 rmarkdown::html_document:
  toc: true
  toc_float: true
  number_sections: false
  theme: spacelab
  highlight: pygments
vignette: >
 %\VignetteIndexEntry{The R Package S3PL: A Tutorial}
 %\VignetteEngine{knitr::rmarkdown}
 %\VignetteEncoding{UTF-8}
---

# Preliminaries

Load the package S3PL

```{r}
library("S3PL")
```

and simulate a dataset from a 3PL model.

```{r}
set.seed(1)
dataset <- simtpl(n = 1000, diff = rnorm(30), discr = rbeta(30, 3, 3) * 0.6 + 0.7, 
                            guess = rbeta(30, 3, 5) * 0.4)
```

# Estimation

## Penalized maximum likelihood 

Estimate the item parameters using penalized maximum likelihood estimation.
The maximum likelihood estimates are computed by default.
The vector of tuning parameters is specified in `lambda`.
If `cv` is `TRUE`, K-fold cross-validation is performed to select
the tuning parameter. The default number of folds is 5, which can be 
changed using argument `K`.

```{r,message = FALSE}
mod <- tpl(data = dataset, penalized = TRUE, lambda = seq(0.01, 0.5, by = 0.01), cv = TRUE)
mod
```

The estimates are given in the usual IRT parameterization:
$$
p_{ij}={\rm Pr}(X_{ij}=1| \theta_i;a_j,b_j,c_j) =
c_j+(1-c_j)\frac{\exp\{ a_j(\theta_i-b_{j})\}}{1+\exp \{ a_j(\theta_i-b_{j}) \}}.
$$

The parameterization used to estimate the parameters is the following:
$$
\pi_{ij}=F(\beta_{3j})+\{1-F(\beta_{3j})\}\frac{\exp (\beta_{1j}+\beta_{2j}\theta_i)}
{1+\exp (\beta_{1j}+\beta_{2j}\theta_i)}
$$
with
$$
F(\beta_{3j})=\frac{\exp(\beta_{3j})}{1+\exp(\beta_{3j})} \, .
$$
To display the estimates using this parameterization set `IRTparam = FALSE`.

```{r}
print(mod, IRTparam = FALSE)
```

### Plot the results

The `plot` function displays the results on a graph.
The first plot shows the cross-validation error agains $\lambda$.
The other graphs show the regularization path for each type of parameter.
By default, only the guessing parameters are shown using the IRT parameterization.

```{r, fig.width=10, fig.height=5}
plot(mod)
```

To plot the estimates using the parameterization used for estimation
set `IRTparam = FALSE`.

```{r, fig.width=10, fig.height=5}
plot(mod, IRTparam = FALSE)
```

To show the other parameters set `onlyGuess = FALSE`.

```{r, fig.width=10, fig.height=10}
plot(mod, onlyGuess = FALSE)
```

Setting both arguments to `FALSE`, all parameters are plotted
using the parameterization used for estimation.

```{r, fig.width=10, fig.height=10}
plot(mod, IRTparam = FALSE, onlyGuess = FALSE)
```




## Bias reduction methodology

Estimate the parameters using the bias reduction methodology, and two cores.

```{r,message = FALSE}
modBR <- tpl(data = dataset, BR = TRUE, ncores = 2)
modBR
print(modBR, IRTparam = FALSE)
```

The empirical approximation is used by default.
To use the Monte Carlo approximation set `empirical` to `FALSE`.
The number of replications for the Monte Carlo approximation 
are speficied in argument `M` and are set to 5000 by default.



